### 2019-02-11 tex_v2/manuscript.tex
conclusions done

	\section{Conclusions}
	%word count: (3157 so far...)
	%Par 1 - Microstructure
	%Par 2 - Tensile and fatigue
	%Par 3 - Fracture
	%Par 4 - Wrap-up
		The rostrum of \textit{Curculio} is characterized by a discontinuous composite profile, wherein the cuticle is strongly differentiated along an anterior-posterior gradient.
		In particular, the cuticle in the apical portion of the rostrum exhibits marked reduction in relative thickness of the and in stacking-angle between pseudo-orthogonal plies of the endocuticle, which are aligned at $\pm45\degree$ to the longitudinal axis of the snout.
		Constitutive models demonstrated that an idealized apical cuticle could theoretically achieve 72\% and 60\% reductions in the effective longitudinal membrane and flexural moduli, respectively, compared to the cuticle of the head capsule, thus accounting for the observed flexibility of the rostral apex in live specimens. However, these reductions could only be realized with both modifications to the cuticle, which have a non-additive effect on cuticle elasticity.
		Tensile testing data revealed that increased endocuticle thickness enhances the fracture toughness of the cuticle, raising the intriguing possibility that this system evolved via negative selection of breakage, rather than positive selection of flexibility.

		We confirmed that altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant, and .

		Based on fractographic analysis of test-specimens, we infer that the endocuticle deforms viscoelastically along the longitudinal axes of the macrofibers under uniaxial tension, causing ply-splitting and delamination at high strain.
		The overlying exocuticle then exhibits brittle fracture, at a comparatively low strain, due to shearing between the stretching endocuticle fibers to which it is anchored.
		This outcome is consistent with behavior shown in previous studies and is congruent with theoretical consideration of cuticle microstructure in CLPT, which predicts extension shear-coupling ($A_{16}, A_{26}\neq{0}$) for individual off-axis macrofiber laminae.

		To the best of our knowledge... had not previously been reported

>>>>

	\section{Conclusions}
	%word count: (3176 so far...)

		The rostrum of \textit{Curculio} is characterized by a discontinuous composite profile, wherein the cuticle is strongly differentiated along an anterior-posterior gradient.
		In particular, the cuticle in the apical portion of the rostrum exhibits marked reduction in relative thickness of the and in stacking-angle between pseudo-orthogonal plies of the endocuticle, which are aligned at $\pm45\degree$ to the longitudinal axis of the snout.
		Constitutive models demonstrated that an idealized apical cuticle could theoretically achieve 72\% and 60\% reductions in the effective longitudinal membrane and flexural moduli, respectively, compared to the cuticle of the head capsule, thus accounting for the observed flexibility of the rostral apex in live specimens.
		However, these reductions can only be realized with both modifications to the cuticle, which have a non-additive effect on cuticle elasticity, implying that these weevils require both modifications to function properly during oviposition.

		Our tensile testing data revealed that increased endocuticle thickness correlates with greater fracture strength of the cuticle, while increased stiffness was associated with lower failure strains and reduced fracture toughness.
		Additionally, fatigue testing of a highly-curved rostrum confirmed that the apical portion of the snout can be subjected to repeated antero-dorsal flexion without evidence of damage.
		We therefore conclude that the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant, and that this profile allows the rostrum to be flexed into a completely straight configuration without exceeding the elastic limits of the cuticle.
		Because these associations were independent of species membership, we posit that the behavior of the cuticle is consistent across the genus, and that rostral flexibility is achieved exclusively through a modified cuticle lay-up in all \textit{Curculio} species.

		Based on fractographic analysis of the test-specimens, we infer that the endocuticle deforms viscoelastically along the longitudinal axes of the macrofibers under uniaxial tension, causing ply-splitting and delamination at high strain.
		However, the overlying exocuticle exhibits brittle fracture at a comparatively lower strain, due to shearing between the stretching endocuticle fibers to which it is anchored.
		This outcome is consistent with behavior shown in previous studies and is congruent with theoretical consideration of cuticle microstructure in CLPT, which predicts extension shear-coupling ($A_{16}, A_{26}\neq{0}$) for individual off-axis macrofiber laminae.
		Based on this pattern of fracture behavior, we identified the exocuticle-rich occipital suture as a common point of void nucleation and crack initiation.

		From a biological perspective, these findings reveal an unexpected morphological source of evolutionary constraint on rostral flexibility, raising the intriguing possibility that this system evolved primarily via negative selection of fracture, rather than positive selection of flexibility.
		In particular, the cuticle is invaginated in precisely the portion of the snout that experiences the greatest degree of tension during antero-dorsal flexion; the doubly-thick exocuticle in the invagination thus creates an unavoidable, brittle weak-point in the otherwise endocuticle-dominated rostral apex.
		This constraint, as well as the minimization of exocuticle thickness in the rostral apex, and the increased toughness derived from a thickened endocuticle, all point to avoidance of catastrophic structural failure as a driving selective pressure in the evolution of the rostrum.
